---
title: "rstats AOC Leaderboard"
description: |
  An Advent of Code Leaderboard for the #rstats community sorted by total stars and average time to complete.
site: distill::distill_website
---

Last updated: `r lubridate::now("EST")` EST

## About

This leaderboard sorts by total number of stars and then by mean time between part one and part two of the puzzles. 

The goal is to de-emphasize the effect of starting the puzzle closer to the midnight EST release time in favour of an efficient solution for part two (generally the harder of the two puzzles).

In an ideal world I'd have liked to calculate time from when you first download the input or open the puzzle description page, but unfortunately that is not tracked!

If you have any questions, please send me a DM on [Twitter](https://twitter.com/_TanHo) or [Mastodon](https://fosstodon.org/@tanho).

## Leaderboard

```{r setup, include = FALSE}
suppressPackageStartupMessages({
  library(dplyr)
  library(tidyr)
  library(lubridate)
  library(fontawesome)
  library(httr)
  library(reactable)
})

options(dplyr.summarise.inform = FALSE)
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo = FALSE, layout = "l-page", fig.width = 16, fig.height = 16}
get_stars <- function(){
  stars <- httr::GET("https://adventofcode.com/2022/leaderboard/private/view/1032765.json",
                     httr::accept_json(),
                     httr::user_agent("rstats aoc leaderboard https://github.com/tanho63/aoc.leaderboard"),
                     httr::set_cookies(session = Sys.getenv("AOC_COOKIE"))) %>% 
    content() %>% 
    as_tibble() %>% 
    hoist("members",
          "user_name"="name",
          "user_id"="id",
          "aoc_score"="local_score",
          "completed_stars"="completion_day_level",
          "total_stars" = "stars"
    )

  if(sum(stars$total_stars) == 0) {
    message("No stars completed yet!")
    return(NULL)
  }
  
  stars1 <- stars |>   
    unnest_longer('completed_stars', indices_to = "day") %>% 
    unnest_longer("completed_stars", indices_to = "star") %>% 
    hoist(completed_stars, "timestamp" = "get_star_ts") |> 
    select("user_name","user_id","aoc_score","total_stars","day","star","timestamp") %>%
    filter(!is.na(star)) %>% 
    group_by(user_name, user_id) |> 
    mutate(
      aoc_score = min(aoc_score),
      total_stars = max(total_stars)
    ) |> 
    group_by(user_name, user_id, aoc_score, total_stars, day, star) |> 
    summarise(
      timestamp = min(timestamp)
    ) |> 
    ungroup() |> 
    pivot_wider(names_from = star, values_from = timestamp, names_glue = "star{star}_ts") %>% 
    mutate_at(c("star1_ts","star2_ts"),~ as.numeric(.x) %>% lubridate::as_datetime(tz = "America/Toronto")) %>% 
    mutate(time_to_star2 = (star2_ts-star1_ts) %>% round(1)) %>% 
    arrange(desc(as.numeric(day))) %>% 
    select(user_name,total_stars,aoc_score,day,star1_ts,star2_ts,everything())  
  
  return(stars1)
}

get_leaderboard <- function(stars) {
  
  if(is.null(stars)) return(NULL)
  
  leaderboard <- stars %>% 
    group_by(user_name,user_id,aoc_score,total_stars) %>% 
    summarise(
      median_star2 = median(time_to_star2,na.rm = TRUE) %>% `units<-`("mins") %>%  round(1),
      mean_star2 = mean(time_to_star2,na.rm = TRUE) %>% `units<-`("mins") %>% round(1)) %>% 
    ungroup() %>% 
    arrange(desc(total_stars),mean_star2)  
  
  return(leaderboard)
}

stars <- get_stars()
leaderboard <- get_leaderboard(stars)

```
```{r echo = FALSE, layout = "l-page", fig.width = 16, fig.height = 16}
show_leaderboard <- function(leaderboard){
  
  if(is.null(leaderboard)) return("No stars completed yet!")
  
  leaderboard |> 
    select(
      user_name,
      total_stars,
      mean_star2,
      median_star2,
      aoc_score
    ) |> 
    mutate(
      rank = row_number(),
      total_stars = format(total_stars),
      aoc_score = format(aoc_score),
      mean_star2 = format(mean_star2),
      median_star2 = format(median_star2),
      .before = 1
    ) |> 
    reactable(
      # leaderboard,
      columns = list(
        rank = colDef(name = "Rank", minWidth = 75, align = "left"),
        user_name = colDef(name = "User Name", minWidth = 150, html = TRUE),
        total_stars = colDef(name = "Total Stars",
                             minWidth = 75,
                             format = colFormat(suffix = fontawesome::fa("star", fill = "#FABC2A")),
                             align = "center",
                             html = TRUE
        ),
        mean_star2 = colDef(name = "Mean Time", align = "right", minWidth = 75),
        median_star2 = colDef(name = "Median Time", align = "right", minWidth = 75),
        aoc_score = colDef(name = "AOC Score", minWidth = 75, align = "center")
      ),
      striped = TRUE,
      highlight = TRUE,
      resizable = TRUE,
      compact = TRUE,
      fullWidth = TRUE,
      sortable = FALSE,
      searchable = TRUE,
      borderless = TRUE,
      showSortIcon = FALSE,
      defaultPageSize = 100,
      pageSizeOptions = c(50,100,500),
      showPageSizeOptions = TRUE
    )
}
show_leaderboard(leaderboard)

```

